Introducing SCM to a small company

### 2012-01-11 article.tex
tog bort standards

Since it is so hard to write a good SCM plan we will need more help then a helping person.
There are several standards to build a frame or a skeleton upon but one cannot be suitable for all companies, there cannot be one universal standard.
The three most popular are ISO, IEEE and DOD but NASA is also used. \cite{SCMPLAN}
NASA is often used for larger companies and projects and will not be suitable for our small target. The DOD, Department of Defense, standard was used by the military from the beginning but can also be used for companies. We want to have  standard which covers the whole organization and not only the current project, this is however not possible with the DOD standard and we will therefore not use this either.
ISO is a well working standard in industries where we have different management systems and procedures. The Problem Company is a software company with very little or none benefit of such standard.
The standard we will work with is the IEEE which Bounds and Dart measures have the highest rating with a study of 6 criteria (ease of use, completeness, tailorability, consistency, correctness and life cycle connection). IEEE is a very tailorable standard which is good for The Problem Company. There are also more benefits but to choose the standard is not what we want to focus on in this article.

@@

>>>>

@@

-documentation

-source code
